Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Caption 1 tweak.

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} Approximate posteriors on
    $\chieff$ from the Advanced LIGO O1 run observations in
    \citet{O1-BBH}.  We approximate the posteriors reported in
    \citet{O1-BBH} using Gaussians with the same median and 90\%
    credible interval as reported in \citet{O1-BBH}.  It is notable
    that none of the $\chieff$ posteriors extends to the regime of
    high spin magnitudes inferred from several
    electromagnetically-detected stellar-mass black hole systems (see
    \citet{2015PhR...548....1M} for a summary of such measurements).}
\end{figure}

@@

\section{Approximations in the Gravitational Waveform}
The model waveforms used to infer the $\chieff$ of the three LIGO
events incorporate approximations to the true behaviour of the merging
systems that are expected to break down for sufficiently high
mis-aligned spins.  The effect of these approximations on inference on
the parameters describing GW150914 has been investigated in detail
\citep{2016arXiv161107531T} \ilya{[Should be an Abbott et al. ref like
  the others?]}.  For this source, statistical uncertainties dominate
over any waveform systematics.  Detailed comparisons with numerical
relativity computations using no approximations to the dynamics
\citep{2016PhRvD..94f4035A} also suggest that statistical
uncertainties dominate the systematics for this system.
\citet{2016arXiv161107531T} suggests that systematics may dominate for
signals with this large SNR ($\simeq 23$) when the source is edge-on
or has high spins.  The other two events discussed in this paper are
at much lower SNR, with correspondingly larger statistical
uncertainties, and are probably similarly oriented and with similarly
small spins, so we do not expect systematic uncertainties to dominate.

>>>>

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} Approximate posteriors on
    $\chieff$ from the Advanced LIGO O1 run observations in
    \citet{O1-BBH}.  We approximate the posteriors reported in
    \citet{O1-BBH} using Gaussians with the same median and 90\%
    credible interval as reported in \citet{O1-BBH}.  It is notable
    that none of the $\chieff$ posteriors \ilya{supports high \ac{BH}
    spin magnitudes with aligned spins, suggested by observations of stellar-mass black holes in  X-ray binaries} (see
    \citet{2015PhR...548....1M} for a summary of such measurements).}
\end{figure}

@@

\section{Approximations in the Gravitational Waveform}
The model waveforms used to infer the $\chieff$ of the three LIGO
events incorporate approximations to the true behaviour of the merging
systems that are expected to break down for sufficiently high
mis-aligned spins.  The effect of these approximations on inference on
the parameters describing GW150914 has been investigated in detail
\citep{2016arXiv161107531T}.  For this source, statistical uncertainties dominate
over any waveform systematics.  Detailed comparisons with numerical
relativity computations using no approximations to the dynamics
\citep{2016PhRvD..94f4035A} also suggest that statistical
uncertainties dominate the systematics for this system.
\citet{2016arXiv161107531T} suggests that systematics may dominate for
signals with this large SNR ($\simeq 23$) when the source is edge-on
or has high spins.  The other two events discussed in this paper are
at much lower SNR, with correspondingly larger statistical
uncertainties, and are probably similarly oriented and with similarly
small spins, so we do not expect systematic uncertainties to dominate.
